Fig3

### 2020-05-23 analysis/06_datawrangling.Rmd
small chagnes, nothing run'
now with control and bldg, hopefully
gonad bldg still missing

```{r allvsd}
vsd_path <- "../results/DEseq2/hypothesis/"   # path to the data
vsd_files <- dir(vsd_path, pattern = "*vsd.csv") # get file names
vsd_pathfiles <- paste0(vsd_path, vsd_files)
vsd_files

@@

head(allvsd)

library(stringr)
allvsd %>%
  filter(str_detect(samples, "Merc"))

@@

```{R}
write.csv(candidatevsd, "../results/06_candidatevsd.csv", row.names = F)
write.csv(allDEG, "../results/06_allDEG.csv", row.names = F)

candidategenes
```

>>>>

```{r allvsd, message = F, warning  = F}
vsd_path <- "../results/DEseq2/hypothesis/"   # path to the data
vsd_files <- dir(vsd_path, pattern = "*vsd.csv") # get file names
vsd_pathfiles <- paste0(vsd_path, vsd_files)
vsd_files

@@

head(allvsd)
```

@@

```{r write files}
write.csv(candidatevsd, "../results/06_candidatevsd.csv", row.names = F)
write.csv(allDEG, "../results/06_allDEG.csv", row.names = F)

### 2020-05-23 analysis/figure-3.Rmd
small chagnes, nothing run'
gonad bldg still missing

# Figure 4: All things prolactin

@@

```{r}
# candidate counts for boxplots
candidatevsd <- read_csv("../results/06_candidatevsd.csv") %>%
  mutate(treatment = factor(treatment)) %>%
  mutate(tissue = factor(tissue, levels = tissuelevel),
        treatment = factor(treatment, levels = charlevelsnocontrol)) %>%
  drop_na()

@@

```{r savefiles}
write.csv(PRLpit,"../results/PRLvsd.csv", row.names = F)

>>>>

# Figure 3: All things prolactin

@@

```{r}
# candidate counts for boxplots
candidatevsd <- read_csv("../results/06_candidatevsd.csv") %>%
  mutate(treatment = factor(treatment)) %>%
  mutate(tissue = factor(tissue, levels = tissuelevel),
        treatment = factor(treatment, levels = alllevels)) %>%
  drop_na()
head(candidatevsd)

@@

```{r savefiles}
write.csv(PRLpit,"../results/PRLvsd.csv", row.names = F)
```

## PRL and PRLR in three tissues

```{r eval = F}
p1 <- candidateboxplot("hypothalamus", c("PRL"), sexlevels) + labs(subtitle = "hypothalamus", title = "PRL")
p2 <- candidateboxplot("pituitary", c("PRL"), sexlevels) + labs(subtitle = "pituitary")
p3 <- candidateboxplot("gonad", c("PRL"), sexlevels) + labs(subtitle = "gonads") + theme(axis.text.x = element_text(angle = 45))

p4 <- candidateboxplot("hypothalamus", c("PRLR"), sexlevels) + labs(subtitle = " ", title = " ") 
p5 <- candidateboxplot("pituitary", c("PRLR"), sexlevels) + labs(subtitle = " ")
p6 <- candidateboxplot("gonad", c("PRLR"), sexlevels) + theme(axis.text.x = element_text(angle = 45))+ labs(subtitle = " ")

plot_grid(p1,p4,p2,p5,p3,p6, ncol = 2, rel_heights = c(1.2,1,1.2))
